---
title: "t1t2 Developmental Trajectory in Healthy Controls"
author: "Lilly Dipnall"
date: "01/07/2022"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "/Users/cogld/Documents/Thesis/imaging/longitudinal_modelling")
```

```{r,echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/cogld/Documents/Thesis/imaging/longitudinal_modelling")
```

#Load Packages
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggrepel)
library(tidyverse)
library(ggplot2)
library(ggbeeswarm)
library(vioplot)
library(table1)
library(tableone)
library(naniar)
library(expss)
library(Hmisc)
library(gt)
library(glue)
library(devtools)
library(ggpubr)
library(broom)
library(purrr)
library(corrplot)
library(lme4)
library(lmerTest)
library(sjstats)
library(optimx)
library(plm)
library(broom.mixed)
library(Matrix)
library(sjPlot)
library(psych)
library(boot)
library(pscl)
library(cowplot)
library(sjmisc)
library(effects)
library(nlme)

```

#Load Data
```{r,echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("/Users/cogld/Documents/Thesis/imaging/longitudinal_modelling/nicap_data_long_calibrated.csv")
dim(data)
head(data)

data$sex <- as.factor(data$sex)
controls <- data %>%
  dplyr::filter(data$group_dich == "0")

controls <- controls %>% mutate(group = as.factor(group_dich),            
                              wave_nicap = as.factor(wave_nicap),
                              sex = as.factor(sex)) %>%
  mutate(age_c = age - mean(age))
```

#Setting Variables
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#General Variables
sex <- factor(controls$sex)
age <- as.numeric(controls$age)
group <- factor(controls$group_dich)
age_c <- as.numeric(controls$age_c)

#White Matter Tracts
AF_right<-as.numeric(controls$AF_right)
AF_left<-as.numeric(controls$AF_left)
ATR_left<-as.numeric(controls$ATR_left)
ATR_right<-as.numeric(controls$ATR_right)
CA<-as.numeric(controls$CA)
CC<-as.numeric(controls$CC)
CC1<-as.numeric(controls$CC1)
CC2<-as.numeric(controls$CC2)
CC3<-as.numeric(controls$CC3)
CC4<-as.numeric(controls$CC4)
CC5<-as.numeric(controls$CC5)
CC6<-as.numeric(controls$CC6)
CC6<-as.numeric(controls$CC6)
CC7<-as.numeric(controls$CC7)
CG_right<-as.numeric(controls$CG_right)
CG_left<-as.numeric(controls$CG_left)
CST_right<-as.numeric(controls$CST_right)
CST_left<-as.numeric(controls$CST_left)
FPT_right<-as.numeric(controls$FPT_right)
FPT_left<-as.numeric(controls$FPT_left)
FX_right<-as.numeric(controls$FX_right)
FX_left<-as.numeric(controls$FX_left)
ICP_right<-as.numeric(controls$ICP_right)
ICP_left<-as.numeric(controls$ICP_left)
IFO_right<-as.numeric(controls$IFO_right)
IFO_left<-as.numeric(controls$IFO_left)
ILF_right<-as.numeric(controls$ILF_right)
ILF_left<-as.numeric(controls$ILF_left)
MCP<-as.numeric(controls$MCP)
MLF_right<-as.numeric(controls$MLF_right)
MLF_left<-as.numeric(controls$MLF_left)
OR_right<-as.numeric(controls$OR_right)
OR_left<-as.numeric(controls$OR_left)
POPT_right<-as.numeric(controls$POPT_right)
POPT_left<-as.numeric(controls$POPT_left)
SCP_right<-as.numeric(controls$SCP_right)
SCP_left<-as.numeric(controls$SCP_left)
SLF_I_right<-as.numeric(controls$SLF_I_right)
SLF_I_left<-as.numeric(controls$SLF_I_left)
SLF_II_right<-as.numeric(controls$SLF_II_right)
SLF_II_left<-as.numeric(controls$SLF_II_left)
SLF_III_right<-as.numeric(controls$SLF_III_right)
SLF_III_left<-as.numeric(controls$SLF_III_left)
ST_FO_right<-as.numeric(controls$ST_FO_right)
ST_FO_left<-as.numeric(controls$ST_FO_left)
ST_OCC_left<-as.numeric(controls$ST_OCC_left)
ST_OCC_right<-as.numeric(controls$ST_OCC_right)
ST_PAR_right<-as.numeric(controls$ST_PAR_right)
ST_PAR_left<-as.numeric(controls$ST_PAR_left)
ST_POSTC_right<-as.numeric(controls$ST_POSTC_right)
ST_POSTC_left<-as.numeric(controls$ST_POSTC_left)
ST_PREC_right<-as.numeric(controls$ST_PREC_right)
ST_PREC_left<-as.numeric(controls$ST_PREC_left)
ST_PREF_right<-as.numeric(controls$ST_PREF_right)
ST_PREF_left<-as.numeric(controls$ST_PREF_left)
ST_PREM_right<-as.numeric(controls$ST_PREM_right)
ST_PREM_left<-as.numeric(controls$ST_PREM_left)
STR_right<-as.numeric(controls$STR_right)
STR_left<-as.numeric(controls$STR_left)
T_OCC_right<-as.numeric(controls$T_OCC_right)
T_OCC_left<-as.numeric(controls$T_OCC_left)
T_PAR_right<-as.numeric(controls$T_PAR_right)
T_PAR_left<-as.numeric(controls$T_PAR_left)
T_POSTC_right<-as.numeric(controls$T_POSTC_right)
T_POSTC_left<-as.numeric(controls$T_POSTC_left)
T_PREC_right<-as.numeric(controls$T_PREC_right)
T_PREC_left<-as.numeric(controls$T_PREC_left)
T_PREF_right<-as.numeric(controls$T_PREF_right)
T_PREF_left<-as.numeric(controls$T_PREF_left)
T_PREM_right<-as.numeric(controls$T_PREM_right)
T_PREM_left<-as.numeric(controls$T_PREM_left)
UF_right<-as.numeric(controls$UF_right)
UF_left<-as.numeric(controls$UF_left)
```

#Table
```{r,echo=FALSE, warning=FALSE, message=FALSE}
table1 <- table1(~ age_c + sex | wave_nicap, data=controls)
table1
```

#Descriptives Table of WM Tracts
```{r,echo=FALSE, warning=FALSE, message=FALSE}
table2 <- table1(~ AF_right +
AF_left +
ATR_left +
ATR_right +
CA +
CC +
CC1 +
CC2 +
CC3 +
CC4 +
CC5 +
CC6 +
CC6 +
CC7 +
CG_right +
CG_left +
CST_right +
CST_left +
FPT_right +
FPT_left +
FX_right +
FX_left +
ICP_right +
ICP_left +
IFO_right +
IFO_left +
ILF_right +
ILF_left +
MCP +
MLF_right +
MLF_left +
OR_right +
OR_left +
POPT_right +
POPT_left +
SCP_right +
SCP_left +
SLF_I_right +
SLF_I_left +
SLF_II_right +
SLF_II_left +
SLF_III_right +
SLF_III_left +
ST_FO_right +
ST_FO_left +
ST_OCC_left +
ST_OCC_right +
ST_PAR_right +
ST_PAR_left +
ST_POSTC_right +
ST_POSTC_left +
ST_PREC_right +
ST_PREC_left +
ST_PREF_right +
ST_PREF_left +
ST_PREM_right +
ST_PREM_left +
STR_right +
STR_left +
T_OCC_right +
T_OCC_left +
T_PAR_right +
T_PAR_left +
T_POSTC_right +
T_POSTC_left +
T_PREC_right +
T_PREC_left +
T_PREF_right +
T_PREF_left +
T_PREM_right +
T_PREM_left +
UF_right +
UF_left | wave_nicap, data=controls)
table2
```


#-------AF
#*AF Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_AF_left1 <- lme(AF_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_left1)

#age + sex
model_AF_left2 <- lme(AF_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_left2)

#sex*age
model_AF_left3 <- lme(AF_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_left3)
```


#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_AF_left4 <- lme(AF_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_left4)

#age + sex
model_AF_left5 <- lme(AF_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_left5)

#age + sex*age^2
model_AF_left6 <- lme(AF_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
AF_left_model_comp2 <- anova(model_AF_left1, model_AF_left4)
AF_left_model_comp2

AF_left_model_comp3 <- anova(model_AF_left4, model_AF_left5)
AF_left_model_comp3

AF_left_model_comp4 <- anova(model_AF_left5, model_AF_left6)
AF_left_model_comp4
```

#*AF Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_AF_right1 <- lme(AF_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_right1)

#age + sex
model_AF_right2 <- lme(AF_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_right2)

#sex*age
model_AF_right3 <- lme(AF_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_right3)
```



#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_AF_right4 <- lme(AF_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_right4)

#age + sex
model_AF_right5 <- lme(AF_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_right5)

#age + sex*age^2
model_AF_right6 <- lme(AF_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_AF_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
AF_right_model_comp2 <- anova(model_AF_right1, model_AF_right4)
AF_right_model_comp2

AF_right_model_comp3 <- anova(model_AF_right4, model_AF_right5)
AF_right_model_comp3

AF_right_model_comp4 <- anova(model_AF_right5, model_AF_right6)
AF_right_model_comp4
```


#-------ATR
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ATR_left1 <- lme(ATR_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_left1)

#age + sex
model_ATR_left2 <- lme(ATR_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_left2)

#sex*age
model_ATR_left3 <- lme(ATR_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_left3)
```




#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ATR_left4 <- lme(ATR_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_left4)

#age + sex
model_ATR_left5 <- lme(ATR_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_left5)

#age + sex*age^2
model_ATR_left6 <- lme(ATR_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ATR_left_model_comp2 <- anova(model_ATR_left1, model_ATR_left4)
ATR_left_model_comp2

ATR_left_model_comp3 <- anova(model_ATR_left4, model_ATR_left5)
ATR_left_model_comp3

ATR_left_model_comp4 <- anova(model_ATR_left5, model_ATR_left6)
ATR_left_model_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ATR_right1 <- lme(ATR_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_right1)

#age + sex
model_ATR_right2 <- lme(ATR_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_right2)

#sex*age
model_ATR_right3 <- lme(ATR_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_right3)
```


#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ATR_right4 <- lme(ATR_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_right4)

#age + sex
model_ATR_right5 <- lme(ATR_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_right5)

#age + sex*age^2
model_ATR_right6 <- lme(ATR_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ATR_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ATR_right_model_comp2 <- anova(model_ATR_right1, model_ATR_right4)
ATR_right_model_comp2

ATR_right_model_comp3 <- anova(model_ATR_right4, model_ATR_right5)
ATR_right_model_comp3

ATR_right_model_comp4 <- anova(model_ATR_right5, model_ATR_right6)
ATR_right_model_comp4
```


#-------CA
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CA1 <- lme(CA~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CA1)

#age + sex
model_CA2 <- lme(CA~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CA2)

#sex*age
model_CA3 <- lme(CA~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CA3)
```


#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CA4 <- lme(CA~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CA4)

#age + sex
model_CA5 <- lme(CA~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CA5)

#age + sex*age^2
model_CA6 <- lme(CA~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CA6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CA_model_comp2 <- anova(model_CA1, model_CA4)
CA_model_comp2

CA_model_comp3 <- anova(model_CA4, model_CA5)
CA_model_comp3

CA_model_comp4 <- anova(model_CA5, model_CA6)
CA_model_comp4
```

#-------CC
#*1 Rostrum
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC1_1 <- lme(CC1~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC1_1)

#age + sex
model_CC1_2 <- lme(CC1~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC1_2)

#sex*age
model_CC1_3 <- lme(CC1~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC1_3)
```


#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC1_4 <- lme(CC1~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC1_4)

#age + sex
model_CC1_5 <- lme(CC1~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC1_5)

#age + sex*age^2
model_CC1_6 <- lme(CC1~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC1_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC1_model_comp2 <- anova(model_CC1_1, model_CC1_4)
CC1_model_comp2

CC1_model_comp3 <- anova(model_CC1_4, model_CC1_5)
CC1_model_comp3

CC1_model_comp4 <- anova(model_CC1_5, model_CC1_6)
CC1_model_comp4
```


#*2 Genu
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC2_1 <- lme(CC2~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC2_1)

#age + sex
model_CC2_2 <- lme(CC2~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC2_2)

#sex*age
model_CC2_3 <- lme(CC2~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC2_3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC2_4 <- lme(CC2~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC2_4)

#age + sex
model_CC2_5 <- lme(CC2~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC2_5)

#age + sex*age^2
model_CC2_6 <- lme(CC2~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC2_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC2_model_comp2 <- anova(model_CC2_1, model_CC2_4)
CC2_model_comp2

CC2_model_comp3 <- anova(model_CC2_4, model_CC2_5)
CC2_model_comp3

CC2_model_comp4 <- anova(model_CC2_5, model_CC2_6)
CC2_model_comp4
```



#*3 Rostral Body
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC3_1 <- lme(CC3~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC3_1)

#age + sex
model_CC3_2 <- lme(CC3~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC3_2)

#sex*age
model_CC3_3 <- lme(CC3~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC3_3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC3_4 <- lme(CC3~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC3_4)

#age + sex
model_CC3_5 <- lme(CC3~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC3_5)

#age + sex*age^2
model_CC3_6 <- lme(CC3~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC3_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC3_model_comp2 <- anova(model_CC3_1, model_CC3_4)
CC3_model_comp2

CC3_model_comp3 <- anova(model_CC3_4, model_CC3_5)
CC3_model_comp3

CC3_model_comp4 <- anova(model_CC3_5, model_CC3_6)
CC3_model_comp4
```



#*4 Anterior Midbody
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC4_1 <- lme(CC4~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC4_1)

#age + sex
model_CC4_2 <- lme(CC4~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC4_2)

#sex*age
model_CC4_3 <- lme(CC4~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC4_3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC4_4 <- lme(CC4~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC4_4)

#age + sex
model_CC4_5 <- lme(CC4~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC4_5)

#age + sex*age^2
model_CC4_6 <- lme(CC4~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC4_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC4_model_comp2 <- anova(model_CC4_1, model_CC4_4)
CC4_model_comp2

CC4_model_comp3 <- anova(model_CC4_4, model_CC4_5)
CC4_model_comp3

CC4_model_comp4 <- anova(model_CC4_5, model_CC4_6)
CC4_model_comp4
```



#*5 Posterior Midbody
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC5_1 <- lme(CC5~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC5_1)

#age + sex
model_CC5_2 <- lme(CC5~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC5_2)

#sex*age
model_CC5_3 <- lme(CC5~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC5_3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC5_4 <- lme(CC5~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC5_4)

#age + sex
model_CC5_5 <- lme(CC5~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC5_5)

#age + sex*age^2
model_CC5_6 <- lme(CC5~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC5_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC5_model_comp2 <- anova(model_CC5_1, model_CC5_4)
CC5_model_comp2

CC5_model_comp3 <- anova(model_CC5_4, model_CC5_5)
CC5_model_comp3

CC5_model_comp4 <- anova(model_CC5_5, model_CC5_6)
CC5_model_comp4
```


#*6 Isthmus
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC6_1 <- lme(CC6~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC6_1)

#age + sex
model_CC6_2 <- lme(CC6~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC6_2)

#sex*age
model_CC6_3 <- lme(CC6~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC6_3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC6_4 <- lme(CC6~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC6_4)

#age + sex
model_CC6_5 <- lme(CC6~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC6_5)

#age + sex*age^2
model_CC6_6 <- lme(CC6~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC6_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC6_model_comp2 <- anova(model_CC6_1, model_CC6_4)
CC6_model_comp2

CC6_model_comp3 <- anova(model_CC6_4, model_CC6_5)
CC6_model_comp3

CC6_model_comp4 <- anova(model_CC6_5, model_CC6_6)
CC6_model_comp4
```



#*7 Splenium
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CC7_1 <- lme(CC7~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC7_1)

#age + sex
model_CC7_2 <- lme(CC7~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC7_2)

#sex*age
model_CC7_3 <- lme(CC7~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC7_3)
```


#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CC7_4 <- lme(CC7~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC7_4)

#age + sex
model_CC7_5 <- lme(CC7~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC7_5)

#age + sex*age^2
model_CC7_6 <- lme(CC7~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CC7_6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CC7_model_comp2 <- anova(model_CC7_1, model_CC7_4)
CC7_model_comp2

CC7_model_comp3 <- anova(model_CC7_4, model_CC7_5)
CC7_model_comp3

CC7_model_comp4 <- anova(model_CC7_5, model_CC7_6)
CC7_model_comp4
```



#-------CG
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CG_left1 <- lme(CG_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_left1)

#age + sex
model_CG_left2 <- lme(CG_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_left2)

#sex*age
model_CG_left3 <- lme(CG_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CG_left4 <- lme(CG_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_left4)

#age + sex
model_CG_left5 <- lme(CG_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_left5)

#age + sex*age^2
model_CG_left6 <- lme(CG_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CG_leftmodel_comp2 <- anova(model_CG_left1, model_CG_left4)
CG_leftmodel_comp2

CG_leftmodel_comp3 <- anova(model_CG_left4, model_CG_left5)
CG_leftmodel_comp3

CG_leftmodel_comp4 <- anova(model_CG_left5, model_CG_left6)
CG_leftmodel_comp4
```



#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CG_right1 <- lme(CG_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_right1)

#age + sex
model_CG_right2 <- lme(CG_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_right2)

#sex*age
model_CG_right3 <- lme(CG_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CG_right4 <- lme(CG_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_right4)

#age + sex
model_CG_right5 <- lme(CG_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_right5)

#age + sex*age^2
model_CG_right6 <- lme(CG_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CG_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CG_rightmodel_comp2 <- anova(model_CG_right1, model_CG_right4)
CG_rightmodel_comp2

CG_rightmodel_comp3 <- anova(model_CG_right4, model_CG_right5)
CG_rightmodel_comp3

CG_rightmodel_comp4 <- anova(model_CG_right5, model_CG_right6)
CG_rightmodel_comp4
```



#-------CST
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CST_left1 <- lme(CST_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_left1)

#age + sex
model_CST_left2 <- lme(CST_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_left2)

#sex*age
model_CST_left3 <- lme(CST_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CST_left4 <- lme(CST_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_left4)

#age + sex
model_CST_left5 <- lme(CST_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_left5)

#age + sex*age^2
model_CST_left6 <- lme(CST_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CST_leftmodel_comp2 <- anova(model_CST_left1, model_CST_left4)
CST_leftmodel_comp2

CST_leftmodel_comp3 <- anova(model_CST_left4, model_CST_left5)
CST_leftmodel_comp3

CST_leftmodel_comp4 <- anova(model_CST_left5, model_CST_left6)
CST_leftmodel_comp4
```



#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_CST_right1 <- lme(CST_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_right1)

#age + sex
model_CST_right2 <- lme(CST_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_right2)

#sex*age
model_CST_right3 <- lme(CST_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_CST_right4 <- lme(CST_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_right4)

#age + sex
model_CST_right5 <- lme(CST_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_right5)

#age + sex*age^2
model_CST_right6 <- lme(CST_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_CST_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
CST_rightmodel_comp2 <- anova(model_CST_right1, model_CST_right4)
CST_rightmodel_comp2

CST_rightmodel_comp3 <- anova(model_CST_right4, model_CST_right5)
CST_rightmodel_comp3

CST_rightmodel_comp4 <- anova(model_CST_right5, model_CST_right6)
CST_rightmodel_comp4
```



#-------FPT
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_FPT_left1 <- lme(FPT_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_left1)

#age + sex
model_FPT_left2 <- lme(FPT_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_left2)

#sex*age
model_FPT_left3 <- lme(FPT_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_FPT_left4 <- lme(FPT_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_left4)

#age + sex
model_FPT_left5 <- lme(FPT_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_left5)

#age + sex*age^2
model_FPT_left6 <- lme(FPT_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
FPT_leftmodel_comp2 <- anova(model_FPT_left1, model_FPT_left4)
FPT_leftmodel_comp2

FPT_leftmodel_comp3 <- anova(model_FPT_left4, model_FPT_left5)
FPT_leftmodel_comp3

FPT_leftmodel_comp4 <- anova(model_FPT_left5, model_FPT_left6)
FPT_leftmodel_comp4
```



#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_FPT_right1 <- lme(FPT_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_right1)

#age + sex
model_FPT_right2 <- lme(FPT_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_right2)

#sex*age
model_FPT_right3 <- lme(FPT_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_FPT_right4 <- lme(FPT_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_right4)

#age + sex
model_FPT_right5 <- lme(FPT_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_right5)

#age + sex*age^2
model_FPT_right6 <- lme(FPT_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FPT_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
FPT_rightmodel_comp2 <- anova(model_FPT_right1, model_FPT_right4)
FPT_rightmodel_comp2

FPT_rightmodel_comp3 <- anova(model_FPT_right4, model_FPT_right5)
FPT_rightmodel_comp3

FPT_rightmodel_comp4 <- anova(model_FPT_right5, model_FPT_right6)
FPT_rightmodel_comp4
```



#-------FX
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_FX_left1 <- lme(FX_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_left1)

#age + sex
model_FX_left2 <- lme(FX_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_left2)

#sex*age
model_FX_left3 <- lme(FX_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_FX_left4 <- lme(FX_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_left4)

#age + sex
model_FX_left5 <- lme(FX_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_left5)

#age + sex*age^2
model_FX_left6 <- lme(FX_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
FX_leftmodel_comp2 <- anova(model_FX_left1, model_FX_left4)
FX_leftmodel_comp2

FX_leftmodel_comp3 <- anova(model_FX_left4, model_FX_left5)
FX_leftmodel_comp3

FX_leftmodel_comp4 <- anova(model_FX_left5, model_FX_left6)
FX_leftmodel_comp4
```



#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_FX_right1 <- lme(FX_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_right1)

#age + sex
model_FX_right2 <- lme(FX_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_right2)

#sex*age
model_FX_right3 <- lme(FX_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_FX_right4 <- lme(FX_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_right4)

#age + sex
model_FX_right5 <- lme(FX_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_right5)

#age + sex*age^2
model_FX_right6 <- lme(FX_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_FX_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
FX_rightmodel_comp2 <- anova(model_FX_right1, model_FX_right4)
FX_rightmodel_comp2

FX_rightmodel_comp3 <- anova(model_FX_right4, model_FX_right5)
FX_rightmodel_comp3

FX_rightmodel_comp4 <- anova(model_FX_right5, model_FX_right6)
FX_rightmodel_comp4
```


#-------ICP
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ICP_left1 <- lme(ICP_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_left1)

#age + sex
model_ICP_left2 <- lme(ICP_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_left2)

#sex*age
model_ICP_left3 <- lme(ICP_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ICP_left4 <- lme(ICP_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_left4)

#age + sex
model_ICP_left5 <- lme(ICP_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_left5)

#age + sex*age^2
model_ICP_left6 <- lme(ICP_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ICP_leftmodel_comp2 <- anova(model_ICP_left1, model_ICP_left4)
ICP_leftmodel_comp2

ICP_leftmodel_comp3 <- anova(model_ICP_left4, model_ICP_left5)
ICP_leftmodel_comp3

ICP_leftmodel_comp4 <- anova(model_ICP_left5, model_ICP_left6)
ICP_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ICP_right1 <- lme(ICP_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_right1)

#age + sex
model_ICP_right2 <- lme(ICP_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_right2)

#sex*age
model_ICP_right3 <- lme(ICP_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ICP_right4 <- lme(ICP_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_right4)

#age + sex
model_ICP_right5 <- lme(ICP_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_right5)

#age + sex*age^2
model_ICP_right6 <- lme(ICP_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ICP_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ICP_rightmodel_comp2 <- anova(model_ICP_right1, model_ICP_right4)
ICP_rightmodel_comp2

ICP_rightmodel_comp3 <- anova(model_ICP_right4, model_ICP_right5)
ICP_rightmodel_comp3

ICP_rightmodel_comp4 <- anova(model_ICP_right5, model_ICP_right6)
ICP_rightmodel_comp4
```



#-------IFO
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_IFO_left1 <- lme(IFO_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_left1)

#age + sex
model_IFO_left2 <- lme(IFO_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_left2)

#sex*age
model_IFO_left3 <- lme(IFO_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_IFO_left4 <- lme(IFO_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_left4)

#age + sex
model_IFO_left5 <- lme(IFO_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_left5)

#age + sex*age^2
model_IFO_left6 <- lme(IFO_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
IFO_leftmodel_comp2 <- anova(model_IFO_left1, model_IFO_left4)
IFO_leftmodel_comp2

IFO_leftmodel_comp3 <- anova(model_IFO_left4, model_IFO_left5)
IFO_leftmodel_comp3

IFO_leftmodel_comp4 <- anova(model_IFO_left5, model_IFO_left6)
IFO_leftmodel_comp4
```



#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_IFO_right1 <- lme(IFO_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_right1)

#age + sex
model_IFO_right2 <- lme(IFO_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_right2)

#sex*age
model_IFO_right3 <- lme(IFO_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_IFO_right4 <- lme(IFO_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_right4)

#age + sex
model_IFO_right5 <- lme(IFO_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_right5)

#age + sex*age^2
model_IFO_right6 <- lme(IFO_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_IFO_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
IFO_rightmodel_comp2 <- anova(model_IFO_right1, model_IFO_right4)
IFO_rightmodel_comp2

IFO_rightmodel_comp3 <- anova(model_IFO_right4, model_IFO_right5)
IFO_rightmodel_comp3

IFO_rightmodel_comp4 <- anova(model_IFO_right5, model_IFO_right6)
IFO_rightmodel_comp4
```


#-------ILF
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ILF_left1 <- lme(ILF_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_left1)

#age + sex
model_ILF_left2 <- lme(ILF_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_left2)

#sex*age
model_ILF_left3 <- lme(ILF_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ILF_left4 <- lme(ILF_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_left4)

#age + sex
model_ILF_left5 <- lme(ILF_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_left5)

#age + sex*age^2
model_ILF_left6 <- lme(ILF_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ILF_leftmodel_comp2 <- anova(model_ILF_left1, model_ILF_left4)
ILF_leftmodel_comp2

ILF_leftmodel_comp3 <- anova(model_ILF_left4, model_ILF_left5)
ILF_leftmodel_comp3

ILF_leftmodel_comp4 <- anova(model_ILF_left5, model_ILF_left6)
ILF_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ILF_right1 <- lme(ILF_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_right1)

#age + sex
model_ILF_right2 <- lme(ILF_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_right2)

#sex*age
model_ILF_right3 <- lme(ILF_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ILF_right4 <- lme(ILF_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_right4)

#age + sex
model_ILF_right5 <- lme(ILF_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_right5)

#age + sex*age^2
model_ILF_right6 <- lme(ILF_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ILF_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ILF_rightmodel_comp2 <- anova(model_ILF_right1, model_ILF_right4)
ILF_rightmodel_comp2

ILF_rightmodel_comp3 <- anova(model_ILF_right4, model_ILF_right5)
ILF_leftmodel_comp3

ILF_rightmodel_comp4 <- anova(model_ILF_right5, model_ILF_right6)
ILF_rightmodel_comp4
```


#-------MCP
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_MCP1 <- lme(MCP~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MCP1)

#age + sex
model_MCP2 <- lme(MCP~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MCP2)

#sex*age
model_MCP3 <- lme(MCP~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MCP3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_MCP4 <- lme(MCP~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_MCP4)

#age + sex
model_MCP5 <- lme(MCP~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MCP5)

#age + sex*age^2
model_MCP6 <- lme(MCP~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MCP6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
MCPmodel_comp2 <- anova(model_MCP1, model_MCP4)
MCPmodel_comp2

MCPmodel_comp3 <- anova(model_MCP4, model_MCP5)
MCPmodel_comp3

MCPmodel_comp4 <- anova(model_MCP5, model_MCP6)
MCPmodel_comp4
```


#-------MLF
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_MLF_left1 <- lme(MLF_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_left1)

#age + sex
model_MLF_left2 <- lme(MLF_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_left2)

#sex*age
model_MLF_left3 <- lme(MLF_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_MLF_left4 <- lme(MLF_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_left4)

#age + sex
model_MLF_left5 <- lme(MLF_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_left5)

#age + sex*age^2
model_MLF_left6 <- lme(MLF_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
MLF_leftmodel_comp2 <- anova(model_MLF_left1, model_MLF_left4)
MLF_leftmodel_comp2

MLF_leftmodel_comp3 <- anova(model_MLF_left4, model_MLF_left5)
MLF_leftmodel_comp3

MLF_leftmodel_comp4 <- anova(model_MLF_left5, model_MLF_left6)
MLF_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_MLF_right1 <- lme(MLF_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_right1)

#age + sex
model_MLF_right2 <- lme(MLF_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_right2)

#sex*age
model_MLF_right3 <- lme(MLF_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_MLF_right4 <- lme(MLF_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_right4)

#age + sex
model_MLF_right5 <- lme(MLF_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_right5)

#age + sex*age^2
model_MLF_right6 <- lme(MLF_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_MLF_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
MLF_rightmodel_comp2 <- anova(model_MLF_right1, model_MLF_right4)
MLF_rightmodel_comp2

MLF_rightmodel_comp3 <- anova(model_MLF_right4, model_MLF_right5)
MLF_rightmodel_comp3

MLF_rightmodel_comp4 <- anova(model_MLF_right5, model_MLF_right6)
MLF_rightmodel_comp4
```


#-------OR
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_OR_left1 <- lme(OR_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_left1)

#age + sex
model_OR_left2 <- lme(OR_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_left2)

#sex*age
model_OR_left3 <- lme(OR_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_OR_left4 <- lme(OR_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_left4)

#age + sex
model_OR_left5 <- lme(OR_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_left5)

#age + sex*age^2
model_OR_left6 <- lme(OR_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
OR_leftmodel_comp2 <- anova(model_OR_left1, model_OR_left4)
OR_leftmodel_comp2

OR_leftmodel_comp3 <- anova(model_OR_left4, model_OR_left5)
OR_leftmodel_comp3

OR_leftmodel_comp4 <- anova(model_OR_left5, model_OR_left6)
OR_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_OR_right1 <- lme(OR_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_right1)

#age + sex
model_OR_right2 <- lme(OR_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_right2)

#sex*age
model_OR_right3 <- lme(OR_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_OR_right4 <- lme(OR_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_right4)

#age + sex
model_OR_right5 <- lme(OR_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_right5)

#age + sex*age^2
model_OR_right6 <- lme(OR_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_OR_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
OR_rightmodel_comp2 <- anova(model_OR_right1, model_OR_right4)
OR_rightmodel_comp2

OR_rightmodel_comp3 <- anova(model_OR_right4, model_OR_right5)
OR_rightmodel_comp3

OR_rightmodel_comp4 <- anova(model_OR_right5, model_OR_right6)
OR_rightmodel_comp4
```

#-------POPT
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_POPT_left1 <- lme(POPT_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_left1)

#age + sex
model_POPT_left2 <- lme(POPT_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_left2)

#sex*age
model_POPT_left3 <- lme(POPT_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_POPT_left4 <- lme(POPT_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_left4)

#age + sex
model_POPT_left5 <- lme(POPT_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_left5)

#age + sex*age^2
model_POPT_left6 <- lme(POPT_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
POPT_leftmodel_comp2 <- anova(model_POPT_left1, model_POPT_left4)
POPT_leftmodel_comp2

POPT_leftmodel_comp3 <- anova(model_POPT_left4, model_POPT_left5)
POPT_leftmodel_comp3

POPT_leftmodel_comp4 <- anova(model_POPT_left5, model_POPT_left6)
POPT_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_POPT_right1 <- lme(POPT_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_right1)

#age + sex
model_POPT_right2 <- lme(POPT_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_right2)

#sex*age
model_POPT_right3 <- lme(POPT_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_POPT_right4 <- lme(POPT_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_right4)

#age + sex
model_POPT_right5 <- lme(POPT_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_right5)

#age + sex*age^2
model_POPT_right6 <- lme(POPT_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_POPT_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
POPT_rightmodel_comp2 <- anova(model_POPT_right1, model_POPT_right4)
POPT_rightmodel_comp2

POPT_rightmodel_comp3 <- anova(model_POPT_right4, model_POPT_right5)
POPT_rightmodel_comp3

POPT_rightmodel_comp4 <- anova(model_POPT_right5, model_POPT_right6)
POPT_rightmodel_comp4
```


#-------SCP
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SCP_left1 <- lme(SCP_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_left1)

#age + sex
model_SCP_left2 <- lme(SCP_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_left2)

#sex*age
model_SCP_left3 <- lme(SCP_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SCP_left4 <- lme(SCP_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_left4)

#age + sex
model_SCP_left5 <- lme(SCP_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_left5)

#age + sex*age^2
model_SCP_left6 <- lme(SCP_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SCP_leftmodel_comp2 <- anova(model_SCP_left1, model_SCP_left4)
SCP_leftmodel_comp2

SCP_leftmodel_comp3 <- anova(model_SCP_left4, model_SCP_left5)
SCP_leftmodel_comp3

SCP_leftmodel_comp4 <- anova(model_SCP_left5, model_SCP_left6)
SCP_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SCP_right1 <- lme(SCP_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_right1)

#age + sex
model_SCP_right2 <- lme(SCP_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_right2)

#sex*age
model_SCP_right3 <- lme(SCP_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SCP_right4 <- lme(SCP_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_right4)

#age + sex
model_SCP_right5 <- lme(SCP_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_right5)

#age + sex*age^2
model_SCP_right6 <- lme(SCP_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SCP_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SCP_rightmodel_comp2 <- anova(model_SCP_right1, model_SCP_right4)
SCP_rightmodel_comp2

SCP_rightmodel_comp3 <- anova(model_SCP_right4, model_SCP_right5)
SCP_rightmodel_comp3

SCP_rightmodel_comp4 <- anova(model_SCP_right5, model_SCP_right6)
SCP_rightmodel_comp4
```


#-------SLFI
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SLF_I_left1 <- lme(SLF_I_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_left1)

#age + sex
model_SLF_I_left2 <- lme(SLF_I_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_left2)

#sex*age
model_SLF_I_left3 <- lme(SLF_I_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SLF_I_left4 <- lme(SLF_I_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_left4)

#age + sex
model_SLF_I_left5 <- lme(SLF_I_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_left5)

#age + sex*age^2
model_SLF_I_left6 <- lme(SLF_I_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SLF_I_leftmodel_comp2 <- anova(model_SLF_I_left1, model_SLF_I_left4)
SLF_I_leftmodel_comp2

SLF_I_leftmodel_comp3 <- anova(model_SLF_I_left4, model_SLF_I_left5)
SLF_I_leftmodel_comp3

SLF_I_leftmodel_comp4 <- anova(model_SLF_I_left5, model_SLF_I_left6)
SLF_I_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SLF_I_right1 <- lme(SLF_I_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_right1)

#age + sex
model_SLF_I_right2 <- lme(SLF_I_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_right2)

#sex*age
model_SLF_I_right3 <- lme(SLF_I_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SLF_I_right4 <- lme(SLF_I_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_right4)

#age + sex
model_SLF_I_right5 <- lme(SLF_I_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_right5)

#age + sex*age^2
model_SLF_I_right6 <- lme(SLF_I_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_I_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SLF_I_rightmodel_comp2 <- anova(model_SLF_I_right1, model_SLF_I_right4)
SLF_I_rightmodel_comp2

SLF_I_rightmodel_comp3 <- anova(model_SLF_I_right4, model_SLF_I_right5)
SLF_I_rightmodel_comp3

SLF_I_rightmodel_comp4 <- anova(model_SLF_I_right5, model_SLF_I_right6)
SLF_I_rightmodel_comp4
```


#-------SLFII
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SLF_II_left1 <- lme(SLF_II_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_left1)

#age + sex
model_SLF_II_left2 <- lme(SLF_II_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_left2)

#sex*age
model_SLF_II_left3 <- lme(SLF_II_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SLF_II_left4 <- lme(SLF_II_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_left4)

#age + sex
model_SLF_II_left5 <- lme(SLF_II_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_left5)

#age + sex*age^2
model_SLF_II_left6 <- lme(SLF_II_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SLF_II_leftmodel_comp2 <- anova(model_SLF_II_left1, model_SLF_II_left4)
SLF_II_leftmodel_comp2

SLF_II_leftmodel_comp3 <- anova(model_SLF_II_left4, model_SLF_II_left5)
SLF_II_leftmodel_comp3

SLF_II_leftmodel_comp4 <- anova(model_SLF_II_left5, model_SLF_II_left6)
SLF_II_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SLF_II_right1 <- lme(SLF_II_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_right1)

#age + sex
model_SLF_II_right2 <- lme(SLF_II_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_right2)

#sex*age
model_SLF_II_right3 <- lme(SLF_II_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SLF_II_right4 <- lme(SLF_II_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_right4)

#age + sex
model_SLF_II_right5 <- lme(SLF_II_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_right5)

#age + sex*age^2
model_SLF_II_right6 <- lme(SLF_II_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_II_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SLF_II_rightmodel_comp2 <- anova(model_SLF_II_right1, model_SLF_II_right4)
SLF_II_rightmodel_comp2

SLF_II_rightmodel_comp3 <- anova(model_SLF_II_right4, model_SLF_II_right5)
SLF_II_rightmodel_comp3

SLF_II_rightmodel_comp4 <- anova(model_SLF_II_right5, model_SLF_II_right6)
SLF_II_rightmodel_comp4
```


#-------SLFIII
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SLF_III_left1 <- lme(SLF_III_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_left1)

#age + sex
model_SLF_III_left2 <- lme(SLF_III_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_left2)

#sex*age
model_SLF_III_left3 <- lme(SLF_III_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SLF_III_left4 <- lme(SLF_III_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_left4)

#age + sex
model_SLF_III_left5 <- lme(SLF_III_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_left5)

#age + sex*age^2
model_SLF_III_left6 <- lme(SLF_III_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SLF_III_leftmodel_comp2 <- anova(model_SLF_III_left1, model_SLF_III_left4)
SLF_III_leftmodel_comp2

SLF_III_leftmodel_comp3 <- anova(model_SLF_III_left4, model_SLF_III_left5)
SLF_III_leftmodel_comp3

SLF_III_leftmodel_comp4 <- anova(model_SLF_III_left5, model_SLF_III_left6)
SLF_III_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_SLF_III_right1 <- lme(SLF_III_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_right1)

#age + sex
model_SLF_III_right2 <- lme(SLF_III_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_right2)

#sex*age
model_SLF_III_right3 <- lme(SLF_III_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_SLF_III_right4 <- lme(SLF_III_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_right4)

#age + sex
model_SLF_III_right5 <- lme(SLF_III_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_right5)

#age + sex*age^2
model_SLF_III_right6 <- lme(SLF_III_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_SLF_III_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
SLF_III_rightmodel_comp2 <- anova(model_SLF_III_right1, model_SLF_III_right4)
SLF_III_rightmodel_comp2

SLF_III_rightmodel_comp3 <- anova(model_SLF_III_right4, model_SLF_III_right5)
SLF_III_rightmodel_comp3

SLF_III_rightmodel_comp4 <- anova(model_SLF_III_right5, model_SLF_III_right6)
SLF_III_rightmodel_comp4
```


#-------ST_FO
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_FO_left1 <- lme(ST_FO_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_left1)

#age + sex
model_ST_FO_left2 <- lme(ST_FO_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_left2)

#sex*age
model_ST_FO_left3 <- lme(ST_FO_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_FO_left4 <- lme(ST_FO_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_left4)

#age + sex
model_ST_FO_left5 <- lme(ST_FO_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_left5)

#age + sex*age^2
model_ST_FO_left6 <- lme(ST_FO_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_FO_leftmodel_comp2 <- anova(model_ST_FO_left1, model_ST_FO_left4)
ST_FO_leftmodel_comp2

ST_FO_leftmodel_comp3 <- anova(model_ST_FO_left4, model_ST_FO_left5)
ST_FO_leftmodel_comp3

ST_FO_leftmodel_comp4 <- anova(model_ST_FO_left5, model_ST_FO_left6)
ST_FO_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_FO_right1 <- lme(ST_FO_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_right1)

#age + sex
model_ST_FO_right2 <- lme(ST_FO_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_right2)

#sex*age
model_ST_FO_right3 <- lme(ST_FO_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_FO_right4 <- lme(ST_FO_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_right4)

#age + sex
model_ST_FO_right5 <- lme(ST_FO_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_right5)

#age + sex*age^2
model_ST_FO_right6 <- lme(ST_FO_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_FO_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_FO_rightmodel_comp2 <- anova(model_ST_FO_right1, model_ST_FO_right4)
ST_FO_rightmodel_comp2

ST_FO_rightmodel_comp3 <- anova(model_ST_FO_right4, model_ST_FO_right5)
ST_FO_rightmodel_comp3

ST_FO_rightmodel_comp4 <- anova(model_ST_FO_right5, model_ST_FO_right6)
ST_FO_rightmodel_comp4
```


#-------ST_OCC
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_OCC_left1 <- lme(ST_OCC_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_left1)

#age + sex
model_ST_OCC_left2 <- lme(ST_OCC_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_left2)

#sex*age
model_ST_OCC_left3 <- lme(ST_OCC_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_OCC_left4 <- lme(ST_OCC_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_left4)

#age + sex
model_ST_OCC_left5 <- lme(ST_OCC_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_left5)

#age + sex*age^2
model_ST_OCC_left6 <- lme(ST_OCC_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_OCC_leftmodel_comp2 <- anova(model_ST_OCC_left1, model_ST_OCC_left4)
ST_OCC_leftmodel_comp2

ST_OCC_leftmodel_comp3 <- anova(model_ST_OCC_left4, model_ST_OCC_left5)
ST_OCC_leftmodel_comp3

ST_OCC_leftmodel_comp4 <- anova(model_ST_OCC_left5, model_ST_OCC_left6)
ST_OCC_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_OCC_right1 <- lme(ST_OCC_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_right1)

#age + sex
model_ST_OCC_right2 <- lme(ST_OCC_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_right2)

#sex*age
model_ST_OCC_right3 <- lme(ST_OCC_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_OCC_right4 <- lme(ST_OCC_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_right4)

#age + sex
model_ST_OCC_right5 <- lme(ST_OCC_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_right5)

#age + sex*age^2
model_ST_OCC_right6 <- lme(ST_OCC_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_OCC_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_OCC_rightmodel_comp2 <- anova(model_ST_OCC_right1, model_ST_OCC_right4)
ST_OCC_rightmodel_comp2

ST_OCC_rightmodel_comp3 <- anova(model_ST_OCC_right4, model_ST_OCC_right5)
ST_OCC_rightmodel_comp3

ST_OCC_rightmodel_comp4 <- anova(model_ST_OCC_right5, model_ST_OCC_right6)
ST_OCC_rightmodel_comp4
```



#-------ST_PAR
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PAR_left1 <- lme(ST_PAR_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_left1)

#age + sex
model_ST_PAR_left2 <- lme(ST_PAR_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_left2)

#sex*age
model_ST_PAR_left3 <- lme(ST_PAR_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PAR_left4 <- lme(ST_PAR_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_left4)

#age + sex
model_ST_PAR_left5 <- lme(ST_PAR_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_left5)

#age + sex*age^2
model_ST_PAR_left6 <- lme(ST_PAR_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PAR_leftmodel_comp2 <- anova(model_ST_PAR_left1, model_ST_PAR_left4)
ST_PAR_leftmodel_comp2

ST_PAR_leftmodel_comp3 <- anova(model_ST_PAR_left4, model_ST_PAR_left5)
ST_PAR_leftmodel_comp3

ST_PAR_leftmodel_comp4 <- anova(model_ST_PAR_left5, model_ST_PAR_left6)
ST_PAR_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PAR_right1 <- lme(ST_PAR_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_right1)

#age + sex
model_ST_PAR_right2 <- lme(ST_PAR_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_right2)

#sex*age
model_ST_PAR_right3 <- lme(ST_PAR_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PAR_right4 <- lme(ST_PAR_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_right4)

#age + sex
model_ST_PAR_right5 <- lme(ST_PAR_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_right5)

#age + sex*age^2
model_ST_PAR_right6 <- lme(ST_PAR_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PAR_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PAR_rightmodel_comp2 <- anova(model_ST_PAR_right1, model_ST_PAR_right4)
ST_PAR_rightmodel_comp2

ST_PAR_rightmodel_comp3 <- anova(model_ST_PAR_right4, model_ST_PAR_right5)
ST_PAR_rightmodel_comp3

ST_PAR_rightmodel_comp4 <- anova(model_ST_PAR_right5, model_ST_PAR_right6)
ST_PAR_rightmodel_comp4
```


#-------ST_POSTC
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_POSTC_left1 <- lme(ST_POSTC_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_left1)

#age + sex
model_ST_POSTC_left2 <- lme(ST_POSTC_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_left2)

#sex*age
model_ST_POSTC_left3 <- lme(ST_POSTC_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_POSTC_left4 <- lme(ST_POSTC_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_left4)

#age + sex
model_ST_POSTC_left5 <- lme(ST_POSTC_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_left5)

#age + sex*age^2
model_ST_POSTC_left6 <- lme(ST_POSTC_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_POSTC_leftmodel_comp2 <- anova(model_ST_POSTC_left1, model_ST_POSTC_left4)
ST_POSTC_leftmodel_comp2

ST_POSTC_leftmodel_comp3 <- anova(model_ST_POSTC_left4, model_ST_POSTC_left5)
ST_POSTC_leftmodel_comp3

ST_POSTC_leftmodel_comp4 <- anova(model_ST_POSTC_left5, model_ST_POSTC_left6)
ST_POSTC_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_POSTC_right1 <- lme(ST_POSTC_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_right1)

#age + sex
model_ST_POSTC_right2 <- lme(ST_POSTC_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_right2)

#sex*age
model_ST_POSTC_right3 <- lme(ST_POSTC_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_POSTC_right4 <- lme(ST_POSTC_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_right4)

#age + sex
model_ST_POSTC_right5 <- lme(ST_POSTC_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_right5)

#age + sex*age^2
model_ST_POSTC_right6 <- lme(ST_POSTC_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_POSTC_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_POSTC_rightmodel_comp2 <- anova(model_ST_POSTC_right1, model_ST_POSTC_right4)
ST_POSTC_rightmodel_comp2

ST_POSTC_rightmodel_comp3 <- anova(model_ST_POSTC_right4, model_ST_POSTC_right5)
ST_POSTC_rightmodel_comp3

ST_POSTC_rightmodel_comp4 <- anova(model_ST_POSTC_right5, model_ST_POSTC_right6)
ST_POSTC_rightmodel_comp4
```


#-------ST_PREC
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PREC_left1 <- lme(ST_PREC_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_left1)

#age + sex
model_ST_PREC_left2 <- lme(ST_PREC_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_left2)

#sex*age
model_ST_PREC_left3 <- lme(ST_PREC_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PREC_left4 <- lme(ST_PREC_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_left4)

#age + sex
model_ST_PREC_left5 <- lme(ST_PREC_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_left5)

#age + sex*age^2
model_ST_PREC_left6 <- lme(ST_PREC_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PREC_leftmodel_comp2 <- anova(model_ST_PREC_left1, model_ST_PREC_left4)
ST_PREC_leftmodel_comp2

ST_PREC_leftmodel_comp3 <- anova(model_ST_PREC_left4, model_ST_PREC_left5)
ST_PREC_leftmodel_comp3

ST_PREC_leftmodel_comp4 <- anova(model_ST_PREC_left5, model_ST_PREC_left6)
ST_PREC_leftmodel_comp4
```



#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PREC_right1 <- lme(ST_PREC_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_right1)

#age + sex
model_ST_PREC_right2 <- lme(ST_PREC_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_right2)

#sex*age
model_ST_PREC_right3 <- lme(ST_PREC_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PREC_right4 <- lme(ST_PREC_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_right4)

#age + sex
model_ST_PREC_right5 <- lme(ST_PREC_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_right5)

#age + sex*age^2
model_ST_PREC_right6 <- lme(ST_PREC_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREC_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PREC_rightmodel_comp2 <- anova(model_ST_PREC_right1, model_ST_PREC_right4)
ST_PREC_rightmodel_comp2

ST_PREC_rightmodel_comp3 <- anova(model_ST_PREC_right4, model_ST_PREC_right5)
ST_PREC_rightmodel_comp3

ST_PREC_rightmodel_comp4 <- anova(model_ST_PREC_right5, model_ST_PREC_right6)
ST_PREC_rightmodel_comp4
```


#-------ST_PREF
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PREF_left1 <- lme(ST_PREF_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_left1)

#age + sex
model_ST_PREF_left2 <- lme(ST_PREF_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_left2)

#sex*age
model_ST_PREF_left3 <- lme(ST_PREF_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PREF_left4 <- lme(ST_PREF_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_left4)

#age + sex
model_ST_PREF_left5 <- lme(ST_PREF_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_left5)

#age + sex*age^2
model_ST_PREF_left6 <- lme(ST_PREF_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PREF_leftmodel_comp2 <- anova(model_ST_PREF_left1, model_ST_PREF_left4)
ST_PREF_leftmodel_comp2

ST_PREF_leftmodel_comp3 <- anova(model_ST_PREF_left4, model_ST_PREF_left5)
ST_PREF_leftmodel_comp3

ST_PREF_leftmodel_comp4 <- anova(model_ST_PREF_left5, model_ST_PREF_left6)
ST_PREF_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PREF_right1 <- lme(ST_PREF_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_right1)

#age + sex
model_ST_PREF_right2 <- lme(ST_PREF_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_right2)

#sex*age
model_ST_PREF_right3 <- lme(ST_PREF_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PREF_right4 <- lme(ST_PREF_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_right4)

#age + sex
model_ST_PREF_right5 <- lme(ST_PREF_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_right5)

#age + sex*age^2
model_ST_PREF_right6 <- lme(ST_PREF_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREF_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PREF_rightmodel_comp2 <- anova(model_ST_PREF_right1, model_ST_PREF_right4)
ST_PREF_rightmodel_comp2

ST_PREF_rightmodel_comp3 <- anova(model_ST_PREF_right4, model_ST_PREF_right5)
ST_PREF_rightmodel_comp3

ST_PREF_rightmodel_comp4 <- anova(model_ST_PREF_right5, model_ST_PREF_right6)
ST_PREF_rightmodel_comp4
```


#-------ST_PREM
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PREM_left1 <- lme(ST_PREM_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_left1)

#age + sex
model_ST_PREM_left2 <- lme(ST_PREM_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_left2)

#sex*age
model_ST_PREM_left3 <- lme(ST_PREM_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PREM_left4 <- lme(ST_PREM_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_left4)

#age + sex
model_ST_PREM_left5 <- lme(ST_PREM_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_left5)

#age + sex*age^2
model_ST_PREM_left6 <- lme(ST_PREM_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PREM_leftmodel_comp2 <- anova(model_ST_PREM_left1, model_ST_PREM_left4)
ST_PREM_leftmodel_comp2

ST_PREM_leftmodel_comp3 <- anova(model_ST_PREM_left4, model_ST_PREM_left5)
ST_PREM_leftmodel_comp3

ST_PREM_leftmodel_comp4 <- anova(model_ST_PREM_left5, model_ST_PREM_left6)
ST_PREM_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_ST_PREM_right1 <- lme(ST_PREM_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_right1)

#age + sex
model_ST_PREM_right2 <- lme(ST_PREM_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_right2)

#sex*age
model_ST_PREM_right3 <- lme(ST_PREM_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_ST_PREM_right4 <- lme(ST_PREM_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_right4)

#age + sex
model_ST_PREM_right5 <- lme(ST_PREM_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_right5)

#age + sex*age^2
model_ST_PREM_right6 <- lme(ST_PREM_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_ST_PREM_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
ST_PREM_rightmodel_comp2 <- anova(model_ST_PREM_right1, model_ST_PREM_right4)
ST_PREM_rightmodel_comp2

ST_PREM_rightmodel_comp3 <- anova(model_ST_PREM_right4, model_ST_PREM_right5)
ST_PREM_rightmodel_comp3

ST_PREM_rightmodel_comp4 <- anova(model_ST_PREM_right5, model_ST_PREM_right6)
ST_PREM_rightmodel_comp4
```


#-------STR
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_STR_left1 <- lme(STR_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_left1)

#age + sex
model_STR_left2 <- lme(STR_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_left2)

#sex*age
model_STR_left3 <- lme(STR_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_STR_left4 <- lme(STR_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_left4)

#age + sex
model_STR_left5 <- lme(STR_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_left5)

#age + sex*age^2
model_STR_left6 <- lme(STR_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
STR_leftmodel_comp2 <- anova(model_STR_left1, model_STR_left4)
STR_leftmodel_comp2

STR_leftmodel_comp3 <- anova(model_STR_left4, model_STR_left5)
STR_leftmodel_comp3

STR_leftmodel_comp4 <- anova(model_STR_left5, model_STR_left6)
STR_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_STR_right1 <- lme(STR_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_right1)

#age + sex
model_STR_right2 <- lme(STR_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_right2)

#sex*age
model_STR_right3 <- lme(STR_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_STR_right4 <- lme(STR_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_right4)

#age + sex
model_STR_right5 <- lme(STR_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_right5)

#age + sex*age^2
model_STR_right6 <- lme(STR_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_STR_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
STR_rightmodel_comp2 <- anova(model_STR_right1, model_STR_right4)
STR_rightmodel_comp2

STR_rightmodel_comp3 <- anova(model_STR_right4, model_STR_right5)
STR_rightmodel_comp3

STR_rightmodel_comp4 <- anova(model_STR_right5, model_STR_right6)
STR_rightmodel_comp4
```


#-------T_OCC
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_OCC_left1 <- lme(T_OCC_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_left1)

#age + sex
model_T_OCC_left2 <- lme(T_OCC_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_left2)

#sex*age
model_T_OCC_left3 <- lme(T_OCC_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_OCC_left4 <- lme(T_OCC_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_left4)

#age + sex
model_T_OCC_left5 <- lme(T_OCC_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_left5)

#age + sex*age^2
model_T_OCC_left6 <- lme(T_OCC_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_OCC_leftmodel_comp2 <- anova(model_T_OCC_left1, model_T_OCC_left4)
T_OCC_leftmodel_comp2

T_OCC_leftmodel_comp3 <- anova(model_T_OCC_left4, model_T_OCC_left5)
T_OCC_leftmodel_comp3

T_OCC_leftmodel_comp4 <- anova(model_T_OCC_left5, model_T_OCC_left6)
T_OCC_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_OCC_right1 <- lme(T_OCC_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_right1)

#age + sex
model_T_OCC_right2 <- lme(T_OCC_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_right2)

#sex*age
model_T_OCC_right3 <- lme(T_OCC_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_OCC_right4 <- lme(T_OCC_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_right4)

#age + sex
model_T_OCC_right5 <- lme(T_OCC_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_right5)

#age + sex*age^2
model_T_OCC_right6 <- lme(T_OCC_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_OCC_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_OCC_rightmodel_comp2 <- anova(model_T_OCC_right1, model_T_OCC_right4)
T_OCC_rightmodel_comp2

T_OCC_rightmodel_comp3 <- anova(model_T_OCC_right4, model_T_OCC_right5)
T_OCC_rightmodel_comp3

T_OCC_rightmodel_comp4 <- anova(model_T_OCC_right5, model_T_OCC_right6)
T_OCC_rightmodel_comp4
```

#-------T_PAR
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PAR_left1 <- lme(T_PAR_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_left1)

#age + sex
model_T_PAR_left2 <- lme(T_PAR_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_left2)

#sex*age
model_T_PAR_left3 <- lme(T_PAR_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PAR_left4 <- lme(T_PAR_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_left4)

#age + sex
model_T_PAR_left5 <- lme(T_PAR_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_left5)

#age + sex*age^2
model_T_PAR_left6 <- lme(T_PAR_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PAR_leftmodel_comp2 <- anova(model_T_PAR_left1, model_T_PAR_left4)
T_PAR_leftmodel_comp2

T_PAR_leftmodel_comp3 <- anova(model_T_PAR_left4, model_T_PAR_left5)
T_PAR_leftmodel_comp3

T_PAR_leftmodel_comp4 <- anova(model_T_PAR_left5, model_T_PAR_left6)
T_PAR_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PAR_right1 <- lme(T_PAR_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_right1)

#age + sex
model_T_PAR_right2 <- lme(T_PAR_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_right2)

#sex*age
model_T_PAR_right3 <- lme(T_PAR_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PAR_right4 <- lme(T_PAR_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_right4)

#age + sex
model_T_PAR_right5 <- lme(T_PAR_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_right5)

#age + sex*age^2
model_T_PAR_right6 <- lme(T_PAR_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PAR_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PAR_rightmodel_comp2 <- anova(model_T_PAR_right1, model_T_PAR_right4)
T_PAR_rightmodel_comp2

T_PAR_rightmodel_comp3 <- anova(model_T_PAR_right4, model_T_PAR_right5)
T_PAR_rightmodel_comp3

T_PAR_rightmodel_comp4 <- anova(model_T_PAR_right5, model_T_PAR_right6)
T_PAR_rightmodel_comp4
```


#-------T_POSTC
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_POSTC_left1 <- lme(T_POSTC_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_left1)

#age + sex
model_T_POSTC_left2 <- lme(T_POSTC_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_left2)

#sex*age
model_T_POSTC_left3 <- lme(T_POSTC_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_POSTC_left4 <- lme(T_POSTC_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_left4)

#age + sex
model_T_POSTC_left5 <- lme(T_POSTC_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_left5)

#age + sex*age^2
model_T_POSTC_left6 <- lme(T_POSTC_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_POSTC_leftmodel_comp2 <- anova(model_T_POSTC_left1, model_T_POSTC_left4)
T_POSTC_leftmodel_comp2

T_POSTC_leftmodel_comp3 <- anova(model_T_POSTC_left4, model_T_POSTC_left5)
T_POSTC_leftmodel_comp3

T_POSTC_leftmodel_comp4 <- anova(model_T_POSTC_left5, model_T_POSTC_left6)
T_POSTC_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_POSTC_right1 <- lme(T_POSTC_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_right1)

#age + sex
model_T_POSTC_right2 <- lme(T_POSTC_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_right2)

#sex*age
model_T_POSTC_right3 <- lme(T_POSTC_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_POSTC_right4 <- lme(T_POSTC_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_right4)

#age + sex
model_T_POSTC_right5 <- lme(T_POSTC_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_right5)

#age + sex*age^2
model_T_POSTC_right6 <- lme(T_POSTC_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_POSTC_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_POSTC_rightmodel_comp2 <- anova(model_T_POSTC_right1, model_T_POSTC_right4)
T_POSTC_rightmodel_comp2

T_POSTC_rightmodel_comp3 <- anova(model_T_POSTC_right4, model_T_POSTC_right5)
T_POSTC_rightmodel_comp3

T_POSTC_rightmodel_comp4 <- anova(model_T_POSTC_right5, model_T_POSTC_right6)
T_POSTC_rightmodel_comp4
```

#-------T_PREC
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PREC_left1 <- lme(T_PREC_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_left1)

#age + sex
model_T_PREC_left2 <- lme(T_PREC_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_left2)

#sex*age
model_T_PREC_left3 <- lme(T_PREC_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PREC_left4 <- lme(T_PREC_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_left4)

#age + sex
model_T_PREC_left5 <- lme(T_PREC_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_left5)

#age + sex*age^2
model_T_PREC_left6 <- lme(T_PREC_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PREC_leftmodel_comp2 <- anova(model_T_PREC_left1, model_T_PREC_left4)
T_PREC_leftmodel_comp2

T_PREC_leftmodel_comp3 <- anova(model_T_PREC_left4, model_T_PREC_left5)
T_PREC_leftmodel_comp3

T_PREC_leftmodel_comp4 <- anova(model_T_PREC_left5, model_T_PREC_left6)
T_PREC_leftmodel_comp4
```


#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PREC_right1 <- lme(T_PREC_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_right1)

#age + sex
model_T_PREC_right2 <- lme(T_PREC_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_right2)

#sex*age
model_T_PREC_right3 <- lme(T_PREC_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PREC_right4 <- lme(T_PREC_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_right4)

#age + sex
model_T_PREC_right5 <- lme(T_PREC_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_right5)

#age + sex*age^2
model_T_PREC_right6 <- lme(T_PREC_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREC_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PREC_rightmodel_comp2 <- anova(model_T_PREC_right1, model_T_PREC_right4)
T_PREC_rightmodel_comp2

T_PREC_rightmodel_comp3 <- anova(model_T_PREC_right4, model_T_PREC_right5)
T_PREC_rightmodel_comp3

T_PREC_rightmodel_comp4 <- anova(model_T_PREC_right5, model_T_PREC_right6)
T_PREC_rightmodel_comp4
```


#-------T_PREF
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PREF_left1 <- lme(T_PREF_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_left1)

#age + sex
model_T_PREF_left2 <- lme(T_PREF_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_left2)

#sex*age
model_T_PREF_left3 <- lme(T_PREF_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PREF_left4 <- lme(T_PREF_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_left4)

#age + sex
model_T_PREF_left5 <- lme(T_PREF_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_left5)

#age + sex*age^2
model_T_PREF_left6 <- lme(T_PREF_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PREF_leftmodel_comp2 <- anova(model_T_PREF_left1, model_T_PREF_left4)
T_PREF_leftmodel_comp2

T_PREF_leftmodel_comp3 <- anova(model_T_PREF_left4, model_T_PREF_left5)
T_PREF_leftmodel_comp3

T_PREF_leftmodel_comp4 <- anova(model_T_PREF_left5, model_T_PREF_left6)
T_PREF_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PREF_right1 <- lme(T_PREF_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_right1)

#age + sex
model_T_PREF_right2 <- lme(T_PREF_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_right2)

#sex*age
model_T_PREF_right3 <- lme(T_PREF_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PREF_right4 <- lme(T_PREF_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_right4)

#age + sex
model_T_PREF_right5 <- lme(T_PREF_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_right5)

#age + sex*age^2
model_T_PREF_right6 <- lme(T_PREF_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREF_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PREF_rightmodel_comp2 <- anova(model_T_PREF_right1, model_T_PREF_right4)
T_PREF_rightmodel_comp2

T_PREF_rightmodel_comp3 <- anova(model_T_PREF_right4, model_T_PREF_right5)
T_PREF_rightmodel_comp3

T_PREF_rightmodel_comp4 <- anova(model_T_PREF_right5, model_T_PREF_right6)
T_PREF_rightmodel_comp4
```

#-------T_PREM
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PREM_left1 <- lme(T_PREM_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_left1)

#age + sex
model_T_PREM_left2 <- lme(T_PREM_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_left2)

#sex*age
model_T_PREM_left3 <- lme(T_PREM_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PREM_left4 <- lme(T_PREM_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_left4)

#age + sex
model_T_PREM_left5 <- lme(T_PREM_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_left5)

#age + sex*age^2
model_T_PREM_left6 <- lme(T_PREM_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PREM_leftmodel_comp2 <- anova(model_T_PREM_left1, model_T_PREM_left4)
T_PREM_leftmodel_comp2

T_PREM_leftmodel_comp3 <- anova(model_T_PREM_left4, model_T_PREM_left5)
T_PREM_leftmodel_comp3

T_PREM_leftmodel_comp4 <- anova(model_T_PREM_left5, model_T_PREM_left6)
T_PREM_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_T_PREM_right1 <- lme(T_PREM_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_right1)

#age + sex
model_T_PREM_right2 <- lme(T_PREM_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_right2)

#sex*age
model_T_PREM_right3 <- lme(T_PREM_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_T_PREM_right4 <- lme(T_PREM_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_right4)

#age + sex
model_T_PREM_right5 <- lme(T_PREM_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_right5)

#age + sex*age^2
model_T_PREM_right6 <- lme(T_PREM_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_T_PREM_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
T_PREM_rightmodel_comp2 <- anova(model_T_PREM_right1, model_T_PREM_right4)
T_PREM_rightmodel_comp2

T_PREM_rightmodel_comp3 <- anova(model_T_PREM_right4, model_T_PREM_right5)
T_PREM_rightmodel_comp3

T_PREM_rightmodel_comp4 <- anova(model_T_PREM_right5, model_T_PREM_right6)
T_PREM_rightmodel_comp4
```

#-------UF
#*Left
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_UF_left1 <- lme(UF_left~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_left1)

#age + sex
model_UF_left2 <- lme(UF_left~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_left2)

#sex*age
model_UF_left3 <- lme(UF_left~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_left3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_UF_left4 <- lme(UF_left~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_left4)

#age + sex
model_UF_left5 <- lme(UF_left~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_left5)

#age + sex*age^2
model_UF_left6 <- lme(UF_left~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_left6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
UF_leftmodel_comp2 <- anova(model_UF_left1, model_UF_left4)
UF_leftmodel_comp2

UF_leftmodel_comp3 <- anova(model_UF_left4, model_UF_left5)
UF_leftmodel_comp3

UF_leftmodel_comp4 <- anova(model_UF_left5, model_UF_left6)
UF_leftmodel_comp4
```

#*Right
#Linear Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#age 
model_UF_right1 <- lme(UF_right~ age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_right1)

#age + sex
model_UF_right2 <- lme(UF_right~ age_c + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_right2)

#sex*age
model_UF_right3 <- lme(UF_right~ age_c + sex*age_c, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_right3)
```

#Quadratic Model
```{r,echo=FALSE, warning=FALSE, message=FALSE}
model_UF_right4 <- lme(UF_right~ poly(age_c, 2), data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_right4)

#age + sex
model_UF_right5 <- lme(UF_right~ poly(age_c, 2) + sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_right5)

#age + sex*age^2
model_UF_right6 <- lme(UF_right~ poly(age_c, 2) + poly(age_c, 2)*sex, data = controls, random = ~1|id)
sjPlot:: tab_model(model_UF_right6)
```

#Model Comparison 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
#Compare 1 model to 3 model 
UF_rightmodel_comp2 <- anova(model_UF_right1, model_UF_right4)
UF_rightmodel_comp2

UF_rightmodel_comp3 <- anova(model_UF_right4, model_UF_right5)
UF_rightmodel_comp3

UF_rightmodel_comp4 <- anova(model_UF_right5, model_UF_right6)
UF_rightmodel_comp4
```

#*************P-Val Corrections
```{r}
pvals1 <- 
c(0.0000004862711,
0.0000031433330,
0.0000131911800,
0.0000272597200,
0.0000004018912,
0.0013641280000,
0.0001476284000,
0.0001120511000,
0.0000005375215,
0.0000003765112,
0.0000003463650,
0.0000001169898,
0.0000178272900,
0.0000124840900,
0.0000038814420,
0.0000056060530,
0.0000250477600,
0.0000890351900,
0.0000037378560,
0.0000113203700,
0.0000176714900,
0.0007576039000,
0.0000105099000,
0.0000041482180,
0.0000005122018,
0.0000011385470,
0.0000293591700,
0.0000003745453,
0.0000013684230,
0.0000005568588,
0.0000003025683,
0.0000024137450,
0.0000045751160,
0.0000049004050,
0.0000057113250,
0.0000004600764,
0.0000011452950,
0.0000005945103,
0.0000001746724,
0.0000074433640,
0.0000032396990,
0.0000733153100,
0.0002052400000,
0.0000001919868,
0.0000002737366,
0.0000003334854,
0.0000008969103,
0.0000003720010,
0.0000010821400,
0.0000005305336,
0.0000011227980,
0.0000120216700,
0.0000301914000,
0.0000024648140,
0.0000060335660,
0.0000015536340,
0.0000015697860,
0.0000002324918,
0.0022750000000,
0.0000005891079,
0.0000008576902,
0.0000007433224,
0.0000012875450,
0.0000008455692,
0.0000012508370,
0.0000087285880,
0.0000185755400,
0.0000044366780,
0.0000066183180,
0.0000046988630,
0.0000211440700)
fdr_pvals1 <- p.adjust(pvals1, "fdr")
write.csv(fdr_pvals1, file = "fdr_pvals1.csv")

pvals2 <- c(0.6127972000000,
0.5203658000000,
0.4022895000000,
0.5313461000000,
0.3710164000000,
0.2952023000000,
0.3179722000000,
0.5408821000000,
0.3942606000000,
0.5976695000000,
0.6429420000000,
0.5859513000000,
0.2381165000000,
0.5448387000000,
0.4283494000000,
0.3146821000000,
0.2498931000000,
0.3031675000000,
0.2527538000000,
0.5398448000000,
0.2549522000000,
0.2830860000000,
0.5491799000000,
0.5303772000000,
0.4301314000000,
0.6322950000000,
0.3940540000000,
0.7153747000000,
0.7301047000000,
0.6366818000000,
0.5843715000000,
0.6861087000000,
0.4717078000000,
0.7978268000000,
0.4624483000000,
0.6386876000000,
0.6470509000000,
0.6344799000000,
0.4084677000000,
0.5024354000000,
0.4165572000000,
0.4140896000000,
0.4584611000000,
0.4975841000000,
0.6952566000000,
0.7291739000000,
0.5876260000000,
0.7411770000000,
0.7571093000000,
0.5506430000000,
0.4505964000000,
0.3343166000000,
0.5369278000000,
0.6064643000000,
0.5487126000000,
0.2680252000000,
0.3781744000000,
0.5883563000000,
0.1652848000000,
0.8429334000000,
0.5865156000000,
0.9075784000000,
0.7146947000000,
0.4404136000000,
0.3639163000000,
0.2844055000000,
0.5208371000000,
0.7268235000000,
0.7296935000000,
0.7854293000000,
0.7030332000000)

fdr_pvals2 <- p.adjust(pvals2, "fdr")
write.csv(fdr_pvals2, file = "fdr_pvals2.csv")

pvals3 <- c(0.0859836800000,
0.0681198700000,
0.0592328300000,
0.0566045400000,
0.0891864800000,
0.0192738200000,
0.0364036900000,
0.0414789800000,
0.0743687800000,
0.0741192300000,
0.0824444200000,
0.1000949000000,
0.0688801200000,
0.0658477400000,
0.0689021100000,
0.0775617000000,
0.0563586400000,
0.0397486400000,
0.1638298000000,
0.1653167000000,
0.0377140700000,
0.0173050000000,
0.0577292800000,
0.0590274600000,
0.0879181400000,
0.0760238200000,
0.0715636500000,
0.0969862100000,
0.0869044200000,
0.0781339400000,
0.0871306900000,
0.0765658200000,
0.0677743700000,
0.0617171100000,
0.0641221600000,
0.0909218700000,
0.0697047700000,
0.0773875500000,
0.0649761500000,
0.0845031000000,
0.0640766100000,
0.0481933600000,
0.0496593600000,
0.0854866200000,
0.0879036300000,
0.0841810100000,
0.0703377200000,
0.0829355600000,
0.0685889100000,
0.0774811900000,
0.0697182800000,
0.0591478500000,
0.0576507800000,
0.0747616400000,
0.0653329400000,
0.0720425300000,
0.0617373500000,
0.1074397000000,
0.0415456100000,
0.0864720600000,
0.0731720300000,
0.0835463600000,
0.0689125000000,
0.0756474700000,
0.0684676300000,
0.0628962900000,
0.0575591700000,
0.0732322500000,
0.0642312200000,
0.0696260300000,
0.0762086800000)

fdr_pvals3 <- p.adjust(pvals3, "fdr")
write.csv(fdr_pvals3, file = "fdr_pvals3.csv")
```

#*************Scanner Assessment 
```{r,echo=FALSE, warning=FALSE, message=FALSE}
scanner <- read.csv("/Users/cogld/Documents/Thesis/imaging/longitudinal_modelling/scanner_age_match.csv")
dim(scanner)
```
#Shapiro Wilk Tests
```{r,echo=FALSE, warning=FALSE, message=FALSE}
shapiro.test(scanner$AF_right)
shapiro.test(scanner$AF_left)
shapiro.test(scanner$ATR_left)
shapiro.test(scanner$ATR_right)
shapiro.test(scanner$CA)
shapiro.test(scanner$CC)
shapiro.test(scanner$CC1)
shapiro.test(scanner$CC2)
shapiro.test(scanner$CC3)
shapiro.test(scanner$CC4)
shapiro.test(scanner$CC5)
shapiro.test(scanner$CC6)
shapiro.test(scanner$CC6)
shapiro.test(scanner$CC7)
shapiro.test(scanner$CG_right)
shapiro.test(scanner$CG_left)
shapiro.test(scanner$CST_right)
shapiro.test(scanner$CST_left)
shapiro.test(scanner$FPT_right)
shapiro.test(scanner$FPT_left)
shapiro.test(scanner$FX_right)
shapiro.test(scanner$FX_left)
shapiro.test(scanner$ICP_right)
shapiro.test(scanner$ICP_left)
shapiro.test(scanner$IFO_right)
shapiro.test(scanner$IFO_left)
shapiro.test(scanner$ILF_right)
shapiro.test(scanner$ILF_left)
shapiro.test(scanner$MCP)
shapiro.test(scanner$MLF_right)
shapiro.test(scanner$MLF_left)
shapiro.test(scanner$OR_right)
shapiro.test(scanner$OR_left)
shapiro.test(scanner$POPT_right)
shapiro.test(scanner$POPT_left)
shapiro.test(scanner$SCP_right)
shapiro.test(scanner$SCP_left)
shapiro.test(scanner$SLF_I_right)
shapiro.test(scanner$SLF_I_left)
shapiro.test(scanner$SLF_II_right)
shapiro.test(scanner$SLF_II_left)
shapiro.test(scanner$SLF_III_right)
shapiro.test(scanner$SLF_III_left)
shapiro.test(scanner$ST_FO_right)
shapiro.test(scanner$ST_FO_left)
shapiro.test(scanner$ST_OCC_left)
shapiro.test(scanner$ST_OCC_right)
shapiro.test(scanner$ST_PAR_right)
shapiro.test(scanner$ST_PAR_left)
shapiro.test(scanner$ST_POSTC_right)
shapiro.test(scanner$ST_POSTC_left)
shapiro.test(scanner$ST_PREC_right)
shapiro.test(scanner$ST_PREC_left)
shapiro.test(scanner$ST_PREF_right)
shapiro.test(scanner$ST_PREF_left)
shapiro.test(scanner$ST_PREM_right)
shapiro.test(scanner$ST_PREM_left)
shapiro.test(scanner$STR_right)
shapiro.test(scanner$STR_left)
shapiro.test(scanner$T_OCC_right)
shapiro.test(scanner$T_OCC_left)
shapiro.test(scanner$T_PAR_right)
shapiro.test(scanner$T_PAR_left)
shapiro.test(scanner$T_POSTC_right)
shapiro.test(scanner$T_POSTC_left)
shapiro.test(scanner$T_PREC_right)
shapiro.test(scanner$T_PREC_left)
shapiro.test(scanner$T_PREF_right)
shapiro.test(scanner$T_PREF_left)
shapiro.test(scanner$T_PREM_right)
shapiro.test(scanner$T_PREM_left)
shapiro.test(scanner$UF_right)
shapiro.test(scanner$UF_left)
```

#Independant Samples T-tests
```{r,echo=FALSE, warning=FALSE, message=FALSE}
as.factor(scanner$wave_nicap)

t.test(scanner$AF_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$AF_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ATR_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ATR_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CA, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC1, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC2, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC3, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC4, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC5, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC6, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC6, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CC7, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CG_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CG_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CST_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$CST_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$FPT_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$FPT_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$FX_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$FX_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ICP_right, scanner$wave_nicap, paired=FALSE, var.equal=FALSE) #Equal variance Violated so Welch's T-test used
t.test(scanner$ICP_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$IFO_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$IFO_left, scanner$wave_nicap, paired=FALSE, var.equal=FALSE) #Equal variance Violated so Welch's T-test used
t.test(scanner$ILF_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ILF_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$MCP, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$MLF_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$MLF_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$OR_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$OR_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$POPT_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$POPT_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SCP_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SCP_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SLF_I_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SLF_I_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SLF_II_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SLF_II_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SLF_III_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$SLF_III_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_FO_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_FO_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_OCC_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_OCC_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PAR_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PAR_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_POSTC_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_POSTC_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PREC_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PREC_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PREF_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PREF_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PREM_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$ST_PREM_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$STR_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$STR_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_OCC_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_OCC_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PAR_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PAR_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_POSTC_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_POSTC_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PREC_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PREC_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PREF_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PREF_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PREM_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$T_PREM_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$UF_right, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
t.test(scanner$UF_left, scanner$wave_nicap, paired=FALSE, var.equal=TRUE)
```

```{r}
ttest1	<-	t.test(scanner$AF_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest2	<-	t.test(scanner$AF_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest3	<-	t.test(scanner$ATR_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest4	<-	t.test(scanner$ATR_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest5	<-	t.test(scanner$CA, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest6	<-	t.test(scanner$CC, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest7	<-	t.test(scanner$CC1, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest8	<-	t.test(scanner$CC2, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest9	<-	t.test(scanner$CC3, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest10	<-	t.test(scanner$CC4, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest11	<-	t.test(scanner$CC5, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest12	<-	t.test(scanner$CC6, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest13	<-	t.test(scanner$CC7, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest14	<-	t.test(scanner$CG_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest15	<-	t.test(scanner$CG_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest16	<-	t.test(scanner$CST_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest17	<-	t.test(scanner$CST_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest18	<-	t.test(scanner$FPT_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest19	<-	t.test(scanner$FPT_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest20	<-	t.test(scanner$FX_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest21	<-	t.test(scanner$FX_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest22	<-	t.test(scanner$ICP_right, scanner$wave_nicap, paired=TRUE, var.equal=FALSE) #Equal variance Violated so Welch's T-test used
ttest23	<-	t.test(scanner$ICP_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest24	<-	t.test(scanner$IFO_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest25	<-	t.test(scanner$IFO_left, scanner$wave_nicap, paired=TRUE, var.equal=FALSE) #Equal variance Violated so Welch's T-test used
ttest26	<-	t.test(scanner$ILF_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest27	<-	t.test(scanner$ILF_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest28	<-	t.test(scanner$MCP, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest29	<-	t.test(scanner$MLF_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest30	<-	t.test(scanner$MLF_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest31	<-	t.test(scanner$OR_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest32	<-	t.test(scanner$OR_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest33	<-	t.test(scanner$POPT_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest34	<-	t.test(scanner$POPT_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest35	<-	t.test(scanner$SCP_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest36	<-	t.test(scanner$SCP_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest37	<-	t.test(scanner$SLF_I_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest38	<-	t.test(scanner$SLF_I_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest39	<-	t.test(scanner$SLF_II_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest40	<-	t.test(scanner$SLF_II_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest41	<-	t.test(scanner$SLF_III_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest42	<-	t.test(scanner$SLF_III_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest43	<-	t.test(scanner$ST_FO_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest44	<-	t.test(scanner$ST_FO_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest45	<-	t.test(scanner$ST_OCC_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest46	<-	t.test(scanner$ST_OCC_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest47	<-	t.test(scanner$ST_PAR_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest48	<-	t.test(scanner$ST_PAR_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest49	<-	t.test(scanner$ST_POSTC_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest50	<-	t.test(scanner$ST_POSTC_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest51	<-	t.test(scanner$ST_PREC_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest52	<-	t.test(scanner$ST_PREC_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest53	<-	t.test(scanner$ST_PREF_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest54	<-	t.test(scanner$ST_PREF_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest55	<-	t.test(scanner$ST_PREM_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest56	<-	t.test(scanner$ST_PREM_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest57	<-	t.test(scanner$STR_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest58	<-	t.test(scanner$STR_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest59	<-	t.test(scanner$T_OCC_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest60	<-	t.test(scanner$T_OCC_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest61	<-	t.test(scanner$T_PAR_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest62	<-	t.test(scanner$T_PAR_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest63	<-	t.test(scanner$T_POSTC_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest64	<-	t.test(scanner$T_POSTC_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest65	<-	t.test(scanner$T_PREC_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest66	<-	t.test(scanner$T_PREC_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest67	<-	t.test(scanner$T_PREF_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest68	<-	t.test(scanner$T_PREF_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest69	<-	t.test(scanner$T_PREM_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest70	<-	t.test(scanner$T_PREM_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest71	<-	t.test(scanner$UF_right, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)
ttest72	<-	t.test(scanner$UF_left, scanner$wave_nicap, paired=TRUE, var.equal=TRUE)

ttest_tab <- map_df(list(ttest1	,
ttest2,
ttest3,
ttest4,
ttest5,
ttest6,
ttest7,
ttest8,
ttest9,
ttest10,
ttest11,
ttest12,
ttest13,
ttest14,
ttest15,
ttest16,
ttest17,
ttest18,
ttest19,
ttest20,
ttest21,
ttest22,
ttest23,
ttest24,
ttest25,
ttest26,
ttest27,
ttest28,
ttest29,
ttest30,
ttest31,
ttest32,
ttest33,
ttest34,
ttest35,
ttest36,
ttest37,
ttest38,
ttest39,
ttest40,
ttest41,
ttest42,
ttest43,
ttest44,
ttest45,
ttest46,
ttest47,
ttest48,
ttest49,
ttest50,
ttest51,
ttest52,
ttest53,
ttest54,
ttest55,
ttest56,
ttest57,
ttest58,
ttest59,
ttest60,
ttest61,
ttest62,
ttest63,
ttest64,
ttest65,
ttest66,
ttest67,
ttest68,
ttest69,
ttest70,
ttest71,
ttest72), tidy)

write.csv(ttest_tab, file = "ttest_table.csv")
```


